Implementing Adaptive Preregistration with Git and Github

### 2023-10-16 adaptive_preregistration_implementation.qmd
replace images with local files bc links not rendering. rerender

-   View the document in GitHub [here](https://github.com/egouldo/VEFMAP_VEG_Stage6/blob/master/analysis/preregistration_template.Rmd)
-   Click on The 'edit document' button: ![](https://github.com/egouldo/VEFMAP_VEG_Stage6/assets/8400682/dd6ee5b6-9595-46e0-8576-7d2a3c7e2c9a)
-   You will be able to edit the document directly in GitHub, Edit away!

@@

-   If you are finished, or ready to save your changes by 'committing' them, commit by scrolling underneath the document editing window. There will be a box called "commit changes", enter in the commit message box the following:
-   Your message should contain the following: `Initial Preregistration #IssueNumber`. Tag the Preregistration GitHub issue number in the commit message (For this repository, it's `#17`).
-   Fill out the additional description box briefly describing the changes you just made
-   Click "commit"

![](https://github.com/egouldo/VEFMAP_VEG_Stage6/assets/8400682/55fe090c-b72c-45f4-808f-039960796dc0.png)

@@

1.  View the preregistration document in Github, and click on the line-numbers on the left to highlight the PRT item text, as well as your response to the item. For example, let's say you want to start working the model checking, you would highlight the following in the document. Note that once you've highlighted some lines, a little box with an ellipsis appears on top of the lines numbers. ![Screen Shot 2020-05-13 at 1 06 25 pm](https://user-images.githubusercontent.com/8400682/81767208-2d9ad980-951b-11ea-8f59-6d6f583eb155.png)
2.  Click on the tiny box with the ellipsis, and a pop-up dialogue box will appear with 4 options: `Copy lines`, `Copy permalink`, `View git blame`, `References in new issue`. Select the last option `Reference in new issue.` ![Screen Shot 2020-05-13 at 1 06 58 pm](https://user-images.githubusercontent.com/8400682/81767344-80749100-951b-11ea-8b76-1e829528973a.png)
3.  This will open up a new window with a new GitHub Issue for you to complete. Note that part of the issue description has already been filled out for you, this is a reference to the lines you just highlighted: ![Screen Shot 2020-05-13 at 1 07 30 pm](https://user-images.githubusercontent.com/8400682/81767518-ef51ea00-951b-11ea-9398-18fffdcbbeae.png) Which is cool, because if you open the `Preview` tab to view the preview of your issue, it will look like this: ![Screen Shot 2020-05-13 at 1 17 21 pm](https://user-images.githubusercontent.com/8400682/81767585-1c9e9800-951c-11ea-9d2c-46d2faf6368a.png)

>>>>

-   View the document in GitHub [here](https://github.com/egouldo/VEFMAP_VEG_Stage6/blob/master/analysis/preregistration_template.Rmd)
-   Click on The 'edit document' button: ![](figures/edit-document.png)
-   You will be able to edit the document directly in GitHub, Edit away!

@@

-   If you are finished, or ready to save your changes by 'committing' them. There is a box called "commit changes" at the top right of the window, a pop-up window will appear, enter in the commit message box the following:
    -    `Initial Preregistration #IssueNumber`. Tag the Preregistration GitHub issue number in the commit message (For this repository, it's `#17`).
-   Fill out the additional description box briefly describing the changes you just made
-   Ensure that the radio button for creating a new branch is selected, an auto-generated branch name will appear, e.g. `egould-patch-1`.
-   Click "Propose Changes" to start a [pull request](https://docs.github.com/en/get-started/quickstart/github-flow):

![](figures/propose-changes.png)

@@

1.  View the preregistration document in Github, and click on the line-numbers on the left to highlight the PRT item text, as well as your response to the item. For example, let's say you want to start working the model checking, you would highlight the following in the document. Note that once you've highlighted some lines, a little box with an ellipsis appears on top of the lines numbers. ![](figures/highlight-lines.png)
2.  Click on the tiny box with the ellipsis, and a pop-up dialogue box will appear with 4 options: `Copy lines`, `Copy permalink`, `View git blame`, `References in new issue`. Select the last option `Reference in new issue.` ![Screen Shot 2020-05-13 at 1 06 58 pm](figures/reference-in-new-issue.png)
3.  This will open up a new window with a new GitHub Issue for you to complete. Note that part of the issue description has already been filled out for you, this is a reference to the lines you just highlighted: ![](figures/new-issue.png) Which is cool, because if you open the `Preview` tab to view the preview of your issue, it will look like this: ![](figures/preview-new-issue.png)
